Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-07-11 WholePlotTrajectories.Rmd
graphs pimp

keywords: [Taxonomic and Functional Biodiversity, Neotropical Forests, Disturbance Trajectories, Intermediate Disturbance Hypothesis, Long-term Resilience]
journalinfo: Hal xxx
archive: DOI xxxx
date: "`r format(Sys.time(), '%d %B %Y')`"
preamble: >
  \usepackage{textcomp}
  \DeclareUnicodeCharacter{B0}{\textdegree}
  \usepackage{tabu}
  \usepackage{caption}
  \captionsetup{justification = justified}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings re-or-gan-i-za-tion post-dis-tur-bance dis-tur-bance}
bibliography: references.bib
lang: english
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
  bookdown::gitbook: default
  bookdown::word_document2: default
---

@@

```{r Options, echo=FALSE, message=FALSE, warning=F}
knitr::opts_chunk$set(cache=F, warning=F, tidy=TRUE, tidy.opts=list(blank=FALSE, width.cutoff=40), fig.align="center")
# Installation des packages si nécessaire et chargement
Library <- function(Packages) {
  InstallAndLoad <- function(Package) {
    if (!Package %in% installed.packages()[, 1]) {install.packages(Package, repos="https://cran.rstudio.com/")}
    require(Package, character.only = TRUE)
  }
  invisible(sapply(Packages, InstallAndLoad))
}
# Ajouter les packages nécessaires ici
Library("kableExtra")

@@

par(mfrow=c(2,2),mar=c(2,2.5,2.5,1),oma=c(1,2,1,3),no.readonly = T)
TaxoCompo(MatrepTaxo)
mtext("Taxonomic composition",side=3,line=1.8,cex=1.05)
FunCompo(MatrepFun)
mtext("Functional composition",side=3,line=1.8,cex=1.05)
EuclidDist(TaxoEuclid)
mtext("Euclidean distance\nfrom 1985 inventory",side=2,padj=0,line=2,cex=0.8)
mtext("(c)",side=3,adj=0,line=0.5)
EuclidDist(FunEuclid)
mtext("(d)",side=3,adj=0,line=0.5)
mtext("Years since disturbance",side=1,line=2.2,adj=1,cex=0.8)
legend("right",inset=c(-0.35,0),xpd=NA,legend=c("T0","T1","T2","T3"),col=ColorsTr,lwd=2.5,bty="n",title="Treatment")

@@

par(mfrow=c(2,2),mar=c(2,2.5,2.5,1),oma=c(1,2,1,3),no.readonly = T)
TaxoTraj(CompleteTaxo)
plotDiv(CompleteRichFun,remove=TRUE)
mtext("(c) Functional Richness",side=3,adj=0,line=1,cex=0.75)
plotDiv(CompleteFun,remove=TRUE)
mtext("(d) Functional Evenness",side=3,adj=0,line=1,cex=0.75)
mtext("Years since disturbance",side=1,line=2.2,adj=1)
legend("right",inset=c(-0.3,0),xpd=NA,legend=c("T0","T1","T2","T3"),col=ColorsTr,lwd=2.5,bty="n",title="Treatment")

@@

```{r IDHplot, out.width = '100%', echo=FALSE, fig.asp = 1.5/3,fig.cap="Relationship between the initial \\%AGB loss and community taxonmic richness (ref:Bolda), taxonomic evenness (ref:Boldb), functional richness (ref:Boldc),and functional evenness (ref:Boldd) at 10, 20 and 30 years after disturbance. Colors are treatments: green (control), yellow (T1), orange (T2), red (T3) with shaded areas the credibility intervals ", fig.env="figure*"}
load("DB/RichnessIDH");load("DB/SimpsonIDH");load("DB/RaoIDH");load("DB/LostAGB");load("DB/FunRichIDH")

par(mfrow=c(1,4),mar=c(5,2,4,2),oma=c(1,1.5,1,2),no.readonly=TRUE)
plotIDH(Data=Rich,AgbLoss=AGBloss)
mtext("(a) Taxonomic Richness",line=1,side=3,adj=0,cex=0.75)
plotIDH(Data=Sim,AgbLoss=AGBloss)
mtext("(b) Taxonomic Evenness",line=1,side=3,adj=0,cex=0.75)
plotIDH(Data=Rao,AgbLoss=AGBloss)
mtext("(c) Functional richness",line=1,side=3,adj=0,cex=0.75)
plotIDH(Data=FunRich,AgbLoss=AGBloss)
mtext("(d) Functional evenness",line=1,side=3,adj=0,cex=0.75)
mtext("initial AGB loss (%)",side=1,line=2.2,adj=1)
legend("right",inset=c(-0.37,0),xpd=NA,legend=c("10","20","30"),col=colyear,lwd=2.5,bty="n",title="Years")

@@

All disturbed plots had lower functional redundancy than control plots and followed similar hump-shaped trajectories (\@ref(fig:RedFun_rest)). The maximum redundancy loss was positively correlated with the disturbance intensity ($\rho_{spearman}=0.47$) and the initial value had not recovered for any disturbed communities after 30 years.

```{r RedFun_rest, out.width = '100%', echo=FALSE, fig.cap="Trajectories of the functional redundancy within the initial functional space over 30 years after disturbance. Colors are disturbance treatments: green (control), yellow (T1), orange (T2), red (T3) with shaded areas the credibility intervals.", fig.env="figure"}
load("DB/Redundancy_restricted")

par(mar=c(3,2,3,2))
RedundancyPlot(RedundancyTraj_restricted)
mtext("Functional Redundancy",side=3,adj=0,line=1.5,cex=1.2)
mtext("Restricted to initial functional space",side=3,adj=0,cex=0.9,line=0.5)
mtext("Years since disturbance",side=1,line=2.2,adj=1,cex=1.2)

>>>>

keywords: [Taxonomic and Functional Biodiversity, Neotropical Forests, Disturbance Trajectories, Intermediate Disturbance Hypothesis, Long-term Resilience]
journalinfo: Hal xxx
archive: DOI xxxx
date: "`r format(Sys.time(), '%d %B %Y')`"
preamble: >
  \usepackage{textcomp}
  \DeclareUnicodeCharacter{B0}{\textdegree}
  \usepackage{tabu}
  \usepackage{caption}
  \captionsetup{justification = justified}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings re-or-gan-i-za-tion post-dis-tur-bance dis-tur-bance}
bibliography: references.bib
lang: english
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::gitbook: default
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
  bookdown::word_document2: default
---

@@

```{r Options, echo=FALSE, message=FALSE, warning=F}
knitr::opts_chunk$set(cache=F, echo=F,warning=F, tidy=TRUE, tidy.opts=list(blank=FALSE, width.cutoff=40), fig.align="center")
# Installation des packages si nécessaire et chargement
Library <- function(Packages) {
  InstallAndLoad <- function(Package) {
    if (!Package %in% installed.packages()[, 1]) {install.packages(Package, repos="https://cran.rstudio.com/")}
    require(Package, character.only = TRUE)
  }
  invisible(sapply(Packages, InstallAndLoad))
}
# Ajouter les packages nécessaires ici
Library("kableExtra")

@@

par(mfrow=c(2,2),mar=c(2,2.5,2.5,1),oma=c(1,2,1,3),no.readonly = T)
TaxoCompo(MatrepTaxo)
mtext("Taxonomic composition",side=3,line=1.8,cex=1.05)
FunCompo(MatrepFun)
mtext("Functional composition",side=3,line=1.8,cex=1.05)
EuclidDist(TaxoEuclid)
mtext("Euclidean distance\nfrom 1985 inventory",side=2,padj=0,line=2,cex=0.8)
mtext("(c)",side=3,adj=0,line=0.5)
EuclidDist(FunEuclid)
mtext("(d)",side=3,adj=0,line=0.5)
mtext("Years since disturbance",side=1,line=2.2,adj=1,cex=0.8)
legend("right",inset=c(-0.345,0),xpd=NA,legend=c("T0","T1","T2","T3"),col=ColorsTr,lwd=2.5,bty="n",title="Treatment")

@@

par(mfrow=c(2,2),mar=c(2,2.5,2.5,1),oma=c(1,2,1,3),no.readonly = T)
TaxoTraj(CompleteTaxo)
plotDiv(CompleteRichFun,remove=TRUE)
mtext("(c) Functional Richness",side=3,adj=0,line=1,cex=0.9)
plotDiv(CompleteFun,remove=TRUE)
mtext("(d) Functional Evenness",side=3,adj=0,line=1,cex=0.9)
mtext("Years since disturbance",side=1,line=2.2,adj=1)
legend("right",inset=c(-0.3,0),xpd=NA,legend=c("T0","T1","T2","T3"),col=ColorsTr,lwd=2.5,bty="n",title="Treatment")

@@

```{r IDHplot, out.width = '100%', echo=FALSE, fig.asp = 1.5/4,fig.cap="Relationship between the initial \\%AGB loss and community taxonmic richness (ref:Bolda), taxonomic evenness (ref:Boldb), functional richness (ref:Boldc),and functional evenness (ref:Boldd) at 10, 20 and 30 years after disturbance", fig.env="figure*"}
load("DB/RichnessIDH");load("DB/SimpsonIDH");load("DB/RaoIDH");load("DB/LostAGB");load("DB/FunRichIDH")

par(mfrow=c(1,4),mar=c(2,2.5,3,1),oma=c(1,1,1,2.5),no.readonly=TRUE)
plotIDH(Data=Rich,AgbLoss=AGBloss)
mtext("(a) Taxonomic\nRichness",line=1,side=3,adj=0,cex=0.85)
mtext("Equivalent diversity",side=2,line=2.2,adj=1,cex=0.8)
plotIDH(Data=Sim,AgbLoss=AGBloss)
mtext("(b) Taxonomic\nEvenness",line=1,side=3,adj=0,cex=0.85)
plotIDH(Data=Rao,AgbLoss=AGBloss)
mtext("(c) Functional\nRichness",line=1,side=3,adj=0,cex=0.85)
plotIDH(Data=FunRich,AgbLoss=AGBloss)
mtext("(d) Functional\nEvenness",line=1,side=3,adj=0,cex=0.85)
mtext("initial AGB loss (%)",side=1,line=2.2,adj=1,cex=0.8)
legend("right",inset=c(-0.5,0),xpd=NA,legend=c("10","20","30"),col=colyear,lwd=2.5,bty="n",title="Years")

@@

All disturbed plots had lower functional redundancy than control plots and followed similar hump-shaped trajectories (\@ref(fig:RedFunRest)). The maximum redundancy loss was positively correlated with the disturbance intensity ($\rho_{spearman}=0.47$) and the initial value had not recovered for any disturbed communities after 30 years.

```{r RedFunRest, out.width = '100%', echo=FALSE, fig.cap="Trajectories of the functional redundancy within the initial functional space over 30 years after disturbance. Colors are disturbance treatments: green (control), yellow (T1), orange (T2), red (T3) with shaded areas the credibility intervals.", fig.env="figure"}
load("DB/Redundancy_restricted")

par(mar=c(3,2,3,2))
RedundancyPlot(RedundancyTraj_restricted)
mtext("Functional Redundancy",side=3,adj=0,line=1.5,cex=1.5)
mtext("Restricted to initial functional space",side=3,adj=0,cex=1.2,line=0.5)
mtext("Years since disturbance",side=1,line=2.2,adj=1,cex=1.5)

### 2018-07-11 WholePlotTrajectories.tex
graphs pimp

\caption{Relationship between the initial \%AGB loss and community taxonmic richness \textbf{(a)}, taxonomic evenness \textbf{(b)}, functional richness \textbf{(c)},and functional evenness \textbf{(d)} at 10, 20 and 30 years after disturbance. Colors are treatments: green (control), yellow (T1), orange (T2), red (T3) with shaded areas the credibility intervals }\label{fig:IDHplot}
\end{figure*}

@@

All disturbed plots had lower functional redundancy than control plots
and followed similar hump-shaped trajectories (@ref(fig:RedFun\_rest)).
The maximum redundancy loss was positively correlated with the
disturbance intensity (\(\rho_{spearman}=0.47\)) and the initial value
had not recovered for any disturbed communities after 30 years.

@@

{\centering \includegraphics[width=1\linewidth]{WholePlotTrajectories_files/figure-latex/RedFun_rest-1}

@@

\caption{Trajectories of the functional redundancy within the initial functional space over 30 years after disturbance. Colors are disturbance treatments: green (control), yellow (T1), orange (T2), red (T3) with shaded areas the credibility intervals.}(\#fig:RedFun_rest)
\end{figure}

@@

The long-term impact of disturbance on community functional redundancy
meant a lower resilience of the pre-disturbance communities, with higher
chances to see the persistence of disturbance-specific species at the
expense of late-successional ones \citep{Haddad2008}. Besides the
long-term recovery of infrequent species increases the risks to loose
cornerstone species, with unexpected ecological consequences
\citep{Jones1994, Chazdon2003a, Diaz2005, Gardner2007}. Apart from the
functional characteristics considered here, infrequent species might
indeed have unique functions in the ecosystem or be a key for some
fauna.

>>>>

\caption{Relationship between the initial \%AGB loss and community taxonmic richness \textbf{(a)}, taxonomic evenness \textbf{(b)}, functional richness \textbf{(c)},and functional evenness \textbf{(d)} at 10, 20 and 30 years after disturbance}\label{fig:IDHplot}
\end{figure*}

@@

All disturbed plots had lower functional redundancy than control plots
and followed similar hump-shaped trajectories (\ref{fig:RedFunRest}).
The maximum redundancy loss was positively correlated with the
disturbance intensity (\(\rho_{spearman}=0.47\)) and the initial value
had not recovered for any disturbed communities after 30 years.

@@

{\centering \includegraphics[width=1\linewidth]{WholePlotTrajectories_files/figure-latex/RedFunRest-1}

@@

\caption{Trajectories of the functional redundancy within the initial functional space over 30 years after disturbance. Colors are disturbance treatments: green (control), yellow (T1), orange (T2), red (T3) with shaded areas the credibility intervals.}\label{fig:RedFunRest}
\end{figure}

@@

The long-term impact of disturbance on community functional redundancy
meant a lower resilience of the pre-disturbance communities, with higher
chances to see the persistence of disturbance-specific species at the
expense of late-successional ones \citep{Haddad2008}. Besides the
long-term recovery of infrequent species increases the risks to loose
cornerstone species, with unexpected ecological consequences
\citep{Jones1994, Chazdon2003a, Diaz2005}. Apart from the functional
characteristics considered here, infrequent species might indeed have
unique functions in the ecosystem or be a key for some fauna.
